Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-08-19 sections/0intro.tex
..

\documentclass[../text]{subfiles}

@@

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable. It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem*}[\ref{thm:gluing_lcfas}]
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
    \end{equation}
\end{theorem*}
%
The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology. A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}. This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$. Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
\end{document}

>>>>

\documentclass[../text.tex]{subfiles}

@@

\textbf{\Cref{ch:gluing_disk_alg} Collar--gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable. It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem*}[\ref{thm:gluing_lcfas}]
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
    \end{equation}
\end{theorem*}
%
The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology. A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}. This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$. Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.

\end{document}

### 2024-08-19 sections/1stratified.tex
..

\begin{remark}
    A $\bstr$-manifold is a stratified manifold $M$ together with a homotopy-lift $\phi$
    %
    \begin{equation}
        \begin{tikzcd}[column sep = large]
            & \bstr \arrow[d] \\
            \mathsf{Entr}(M) \arrow[ru, "\phi"] \arrow[r, "\tau_M"] & \bsc,
        \end{tikzcd}
    \end{equation}
    %
    i.e., a filler of the $2$-horn in the $\infty$-category $\cat$ of $\infty$-categories  given by $\tau_M$ and $\bstr\to\bsc$.
\end{remark}

@@

\begin{definition}\label{def:collar-gluing}
    A collar-gluing of a stratified manifold $M$ is a weakly constructible bundle $M \xrightarrow{f} [-1,1]$. We denote collar-gluings as
    %
    \begin{equation}
        M \cong M_- \coprod_{M_0 \times \mathbb{R}} M_+,
    \end{equation}
    where $M_- := f^{-1}\left[ -1, 1 \right)$, $M_0 := f^{-1}\{0\}$ and $M_+ := f^{-1} \left( -1, 1 \right]$
\end{definition}

\begin{remark}
    One should think of collar-gluings as analogous to the case of gluing two manifolds with boundary along their boundaries after choosing collars. This is exactly the special thing about them, the overlap region is collared, i.e., looks like a product with $\mathbb{R}$. We also note that the disjoint union is an example of a collar-gluing.
\end{remark}

\begin{theorem}[\cite{aft_localstrut}]\label{thm:decom_strat_man}
    $\mfld(\bstr)$ is generated by $\bstr$ through iteratively forming collar-gluings and taking sequential colimits.
\end{theorem}

@@

    Explaining what exactly we mean by a framed stratified manifold is done in \cite[Example 5.2.12]{aft_localstrut}. According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null-homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$. In more detail, for a general embedded submanifold $\Sigma \xhookrightarrow{} M$ the Gauss map gives the tangent (or equivalently normal) subspace to $\Sigma$ at every point. That is encoded as a map $\Sigma \rightarrow \mathsf{Gr}_d(\mathsf{T}M)$ to the Grassmann bundle of the tangent bundle of $M$. The framing of $M$ is a diffeomorphism of type $\mathsf{T}M\cong M\times\mathbb{R}^n$ over, reducing said map to the Gauss map. A null-homotopy of this map is a trivialization of the tangent as well as the normal bundles of $\Sigma$ in a way that is compatible with the trivialization of the restriction of $\mathsf{T}M$ to $\Sigma$.
\end{remark}

>>>>

\begin{remark}
    A $\bstr$-manifold is a stratified manifold $M$ together with a homotopy--lift $\phi$
    %
    \begin{equation}
        \begin{tikzcd}[column sep = large]
            & \bstr \arrow[d] \\
            \mathsf{Entr}(M) \arrow[ru, "\phi"] \arrow[r, "\tau_M"] & \bsc,
        \end{tikzcd}
    \end{equation}
    %
    i.e., a filler of the $2$-horn in the $\infty$-category $\cat$ of $\infty$-categories  given by $\tau_M$ and $\bstr\to\bsc$.
\end{remark}

@@

\begin{definition}\label{def:collar-gluing}
    A collar-gluing of a stratified manifold $M$ is a weakly constructible bundle $M \xrightarrow{f} [-1,1]$. We denote collar--gluings as
    %
    \begin{equation}
        M \cong M_- \coprod_{M_0 \times \mathbb{R}} M_+,
    \end{equation}
    where $M_- := f^{-1}\left[ -1, 1 \right)$, $M_0 := f^{-1}\{0\}$ and $M_+ := f^{-1} \left( -1, 1 \right]$
\end{definition}

\begin{remark}
    One should think of collar--gluings as analogous to the case of gluing two manifolds with boundary along their boundaries after choosing collars. This is exactly the special thing about them, the overlap region is collared, i.e., looks like a product with $\mathbb{R}$. We also note that the disjoint union is an example of a collar-gluing.
\end{remark}

\begin{theorem}[\cite{aft_localstrut}]\label{thm:decom_strat_man}
    $\mfld(\bstr)$ is generated by $\bstr$ through iteratively forming collar--gluings and taking sequential colimits.
\end{theorem}

@@

    Explaining what exactly we mean by a framed stratified manifold is done in \cite[Example 5.2.12]{aft_localstrut}. According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null--homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$. In more detail, for a general embedded submanifold $\Sigma \xhookrightarrow{} M$ the Gauss map gives the tangent (or equivalently normal) subspace to $\Sigma$ at every point. That is encoded as a map $\Sigma \rightarrow \mathsf{Gr}_d(\mathsf{T}M)$ to the Grassmann bundle of the tangent bundle of $M$. The framing of $M$ is a diffeomorphism of type $\mathsf{T}M\cong M\times\mathbb{R}^n$ over, reducing said map to the Gauss map. A null--homotopy of this map is a trivialization of the tangent as well as the normal bundles of $\Sigma$ in a way that is compatible with the trivialization of the restriction of $\mathsf{T}M$ to $\Sigma$.
\end{remark}

### 2024-08-19 sections/2homology.tex
Todo is partially done.
..

\begin{remark}
    For developing the theory of factorization homology the assumption that $\catC$ has all \emph{sifted}\footnote{Sifted colimits are colimits over a sifted indexing simplicial set $K$, which means that the diagonal functor of $K \neq \emptyset$ is final \[ \mathsf{colim}(K \xrightarrow{} K \times K \xrightarrow{} \catC) \simeq \mathsf{colim}(K \times K \xrightarrow{} \catC).\]} colimits, and the monoidal structure commutes with these, is usually enough. However, if we want the $\infty$-category of algebras valued in $\catC$ to inherit the properties of having sifted colimits that commute with the monoidal structure, then we must require that $\catC$ has \emph{all} (small) colimits. This will similarly be the case for factorization algebras. The stronger requirement also doesn't exclude any of the core examples that we are interested in. In fact, in some situations, the full requirement of presentability makes examples tractable.
\end{remark}

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
\end{example}

@@

More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category: see \cite[Definition 2.1.1.10]{lurie_ha}. For these, \eqref{W1183QD} still holds: see \cite[Remark 2.1.1.14]{lurie_ha}.

@@

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[§5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrizes homotopy-commtuative algebras. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are weakly equivalent. Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

    Now, \cite[§2.4.3]{lurie_ha} contains a construction which associates an $\infty$-operad $\mathscr{C}^{\amalg}$ to any $\infty$-category $\mathscr{C}$ such that $\mathsf{Mul}_{\mathscr{C}^{\amalg}}(x_1\oplus\cdots\oplus x_n; y)\simeq \prod_{\nu=1}^{n}\mathsf{Hom}_{\mathscr{C}}(x_\nu,y)$. If $\mathscr{C}$ is already an $\infty$-operad with a initial unit $0\in\mathscr{C}_{\lrangle{1}}$, then there is (\cite[Lemma 1.20]{aft_fhstrat}) a canonical map of $\infty$-operads $\mathscr{C}\to(\mathscr{C}_{\lrangle{1}})^\amalg$ generalising the idea above.

    We see that piece 1 is in $(\disk(\bstr)_{/M})^{\amalg}$, piece 2 is in $\disk(\bstr)$, and piece (3) describes equivalences in $\disk(\bstr)^{\amalg}$. The full collection is thus in the homotopy pullback $\infty$-operad 
    \[
        \begin{tikzcd}
        \disk(\bstr)_{/M}\ar[r]\ar[d]\arrow[dr, phantom, "\ulcorner", very near start] & (\disk(\bstr)_{/M})^{\amalg}\ar[d]\\
        \disk(\bstr)\ar[r] & \disk(\bstr)^{\amalg}
        \end{tikzcd}.
    \]
    A representative is then the following ordinary iterated fibre product of $\infty$-operads:
    \[
        \disk(\bstr)_{/M}\coloneqq \disk(\bstr)\times_{(\disk(\bstr)^{\amalg})^{\{0\}}}\mathsf{Isom}(\disk(\bstr)^{\amalg})\times_{(\disk(\bstr)^{\amalg})^{\{1\}}}(\disk(\bstr)_{/M})^{\amalg},
    \]
    where $\mathsf{Isom}(\disk(\bstr)^{\amalg})\subset\mathsf{Ar}(\disk(\bstr)^{\amalg})=(\disk(\bstr)^{\amalg})^{\Delta[1]}$ is the full sub-$\infty$-category of the arrow $\infty$-category generated by those morphisms that are isomorphisms in the associated homotopy category, whence the isotopies mentioned in piece 3.

\begin{remark}
    Analogous statements hold for $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ and the resulting $\infty$-operads. The difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e., finite sets of open embeddings into $M$. However, a morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$ such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative as explained above, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose.\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.} 
    Similarly for higher arity-morphisms.
\end{remark}

@@

\begin{construction}\label{con:assocRL}
    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory}, or \emph{(colored) operad}, is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain. The operadic nerve of a topological or Kan-enriched multicategy is an $\infty$-operad: see \cite[Proposition 2.1.1.27]{lurie_ha}.} with three objects $R$, $A$ and $L$. To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$. We have:
    %
    \begin{enumerate}
        \item $\mathsf{Assoc^{RL}}(I, A)$ is empty if either $R$ or $L$ appear on the list $I$; otherwise it is given by the number of total orders of $I$.
        \item $\mathsf{Assoc^{RL}}(I, R)$ is empty if either $L$ appears on the list or $R$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $R$ is a minimum.
        \item $\mathsf{Assoc^{RL}}(I, L)$ is empty if either $R$ appears on the list or $L$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $L$ is a minimum.
    \end{enumerate}
    %
    Composition of multi-morphisms is given by concatenation. 
\end{construction}

>>>>

\begin{remark}
    For developing the theory of factorization homology the assumption that $\catC$ has all \emph{sifted}\footnote{Sifted colimits are colimits over a sifted indexing simplicial set $K$, which means that the diagonal functor of $K \neq \emptyset$ is final \[ \mathsf{colim}(K \xrightarrow{} K \times K \xrightarrow{} \catC) \simeq \mathsf{colim}(K \times K \xrightarrow{} \catC).\]} colimits, and the monoidal structure commutes with these, is usually enough. However, if we want the $\infty$-category of algebras valued in $\catC$ to inherit the properties of having sifted colimits that commute with the monoidal structure, then we must require that $\catC$ has \emph{all} (small) colimits. This will similarly be the case for factorization algebras. The stronger requirement also doesn't exclude any of the core examples that we are interested in. In fact, in some situations, the full requirement of presentability makes examples more tractable.
\end{remark}

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Sp}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
\end{example}

@@

More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalization of the properties of a symmetric monoidal $\infty$-category: see \cite[Definition 2.1.1.10]{lurie_ha}. For these, \eqref{W1183QD} still holds: see \cite[Remark 2.1.1.14]{lurie_ha}.

@@

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[§5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy--associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrizes homotopy--commutative algebras. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are weakly equivalent. Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

    Now, \cite[§2.4.3]{lurie_ha} contains a construction which associates an $\infty$-operad $\mathscr{C}^{\amalg}$ to any $\infty$-category $\mathscr{C}$ such that $\mathsf{Mul}_{\mathscr{C}^{\amalg}}(x_1\oplus\cdots\oplus x_n; y)\simeq \prod_{\nu=1}^{n}\mathsf{Hom}_{\mathscr{C}}(x_\nu,y)$. If $\mathscr{C}$ is already an $\infty$-operad with a initial unit $0\in\mathscr{C}_{\lrangle{1}}$, then there is (\cite[Lemma 1.20]{aft_fhstrat}) a canonical map of $\infty$-operads $\mathscr{C}\to(\mathscr{C}_{\lrangle{1}})^\amalg$ generalizing the idea above.

    We see that piece 1 is in $(\disk(\bstr)_{/M})^{\amalg}$, piece 2 is in $\disk(\bstr)$, and piece (3) describes equivalences in $\disk(\bstr)^{\amalg}$. The full collection is thus in the homotopy pullback $\infty$-operad 
    \[
        \begin{tikzcd}
        \disk(\bstr)_{/M}\ar[r]\ar[d]\arrow[dr, phantom, "\ulcorner", very near start] & (\disk(\bstr)_{/M})^{\amalg}\ar[d]\\
        \disk(\bstr)\ar[r] & \disk(\bstr)^{\amalg}
        \end{tikzcd}.
    \]
    A representative is then the following ordinary iterated fiber product of $\infty$-operads:
    \[
        \disk(\bstr)_{/M}\coloneqq \disk(\bstr)\times_{(\disk(\bstr)^{\amalg})^{\{0\}}}\mathsf{Isom}(\disk(\bstr)^{\amalg})\times_{(\disk(\bstr)^{\amalg})^{\{1\}}}(\disk(\bstr)_{/M})^{\amalg},
    \]
    where $\mathsf{Isom}(\disk(\bstr)^{\amalg})\subset\mathsf{Ar}(\disk(\bstr)^{\amalg})=(\disk(\bstr)^{\amalg})^{\Delta[1]}$ is the full sub-$\infty$-category of the arrow $\infty$-category generated by those morphisms that are isomorphisms in the associated homotopy category, whence the isotopies mentioned in piece 3.

\begin{remark}
    Analogous statements hold for $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ and the resulting $\infty$-operads. The difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e., finite sets of open embeddings into $M$. However, a morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$ such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative as explained above, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}. Similarly for higher arity morphisms.
\end{remark}

@@

\begin{construction}\label{con:assocRL}
    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory}, or \emph{(colored) operad}, is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain. The operadic nerve of a topological or Kan-enriched multicategory is an $\infty$-operad: see \cite[Proposition 2.1.1.27]{lurie_ha}.} with three objects $R$, $A$ and $L$. To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$. We have:
    %
    \begin{enumerate}
        \item $\mathsf{Assoc^{RL}}(I, A)$ is empty if either $R$ or $L$ appear on the list $I$; otherwise it is given by the number of total orders of $I$.
        \item $\mathsf{Assoc^{RL}}(I, R)$ is empty if either $L$ appears on the list or $R$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $R$ is a minimum.
        \item $\mathsf{Assoc^{RL}}(I, L)$ is empty if either $R$ appears on the list or $L$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $L$ is a minimum.
    \end{enumerate}
    %
    Composition of multi-morphisms is given by concatenation. 
\end{construction}

### 2024-08-19 sections/3algebras.tex
..

\subsection{The \texorpdfstring{$\infty$-}{infinity }operad of Factorization Algebras}

@@

    for each $\iota \in \disk_{/M}$, an open embedding of disks in $M$, and these morphisms are now maps of spaces which we want to show are equivalences. We now study the hom-spaces appearing above. By definition of the slice $\infty$-category, the hom-spaces are given as the homotopy fibers

@@

    where the notation $M_{[B]}$ denotes the $[B]$-stratum of $M$ (see \cite[Prop.4.4.7]{aft_localstrut}). We also note that under these equivalences the map $e^*$ is given by $\coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(e_{[B]})$, which is even an open inclusion. Thus, the hom-spaces of the slice $\infty$-category are given as 

@@

    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}. In this language, first we have to provide, for each locally constant factorization algebra in two variables $\int_{-}(\int_{-} A) \in \lcfa_{X}(\lcfa_{Y}(\catC))$, a locally constant factorization algebra $\int_{-} \bar{A} \in \lcfa_{X \times Y} (\catC)$ and an equivalence
    %
    \begin{equation}
        \bar{\pi} \int_{-} \bar{A} \xrightarrow[\simeq]{\ \ \phi \ \ } \int_{-} \big( \int_{-} A \big).
    \end{equation}
    %
    This is an equivalence in $\lcfa_{X}(\lcfa_{Y}(\catC))$, which means that it is a family of equivalences $\phi(U,V)$ in $\catC$
    %
    \begin{equation}
        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{U} \big( \int_{V} A \big),
    \end{equation}
    %
    one for each open $U \subset X$, and each open $V \subset Y$. Furthermore, this family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf. \Cref{rem:unpack_pfac_def}). Such a family of equivalences is provided by the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology, which pointwise gives us the equivalences $\phi(U,V)$. As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure dues to the equivalences
    %
    \begin{equation}
        \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{U_i},
    \end{equation}
    %
    together with the colimit preserving property of the monoidal product of $\catC$. This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{pi}$ is essentially surjective. Moreover, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural (or rather functorial) in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}

>>>>

\subsection{The \texorpdfstring{$\infty$-}{infinity-}operad of Factorization Algebras}

@@

    for each $\iota \in \disk_{/M}$, an open embedding of disks in $M$, and these morphisms are now maps of spaces which we want to show are equivalences. We now study the hom--spaces appearing above. By definition of the slice $\infty$-category, the hom--spaces are given as the homotopy fibers

@@

    where the notation $M_{[B]}$ denotes the $[B]$-stratum of $M$ (see \cite[Prop.4.4.7]{aft_localstrut}). We also note that under these equivalences the map $e^*$ is given by $\coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(e_{[B]})$, which is even an open inclusion. Thus, the hom--spaces of the slice $\infty$-category are given as 

@@

    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}. In this language, first we have to provide, for each locally constant factorization algebra in two variables $\int_{-}(\int_{-} A) \in \lcfa_{X}(\lcfa_{Y}(\catC))$, a locally constant factorization algebra $\int_{-} \bar{A} \in \lcfa_{X \times Y} (\catC)$ and an equivalence
    %
    \begin{equation}
        \bar{\pi} \int_{-} \bar{A} \xrightarrow[\simeq]{\ \ \phi \ \ } \int_{-} \big( \int_{-} A \big).
    \end{equation}
    %
    This is an equivalence in $\lcfa_{X}(\lcfa_{Y}(\catC))$, which means that it is a family of equivalences $\phi(U,V)$ in $\catC$
    %
    \begin{equation}
        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{V} \big( \int_{U} A \big),
    \end{equation}
    %
    one for each open $U \subset X$, and each open $V \subset Y$, such that the family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf. \Cref{rem:unpack_pfac_def}). Such a family of equivalences is provided by the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology, which pointwise gives us the equivalences $\phi(U,V)$.

    ...

    As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure %due to the equivalences
    %%
    %\begin{equation}
    %    \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{/U_i},
    %\end{equation}
    %%
    %together with the colimit preserving property of the monoidal product of $\catC$. This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{\pi}$ is essentially surjective.

    Finally, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural (or rather functorial) in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}
